Positive Relationship between a Country's Employment Rate and Permanent Immigrant Inflows

### 2023-04-18 outputs/paper/paper.qmd
commit
Commit

@@

merged_data |>
  mutate(Permanent_Inflows_Rate = (Permanent_Inflows / Population) * 100) |>
  group_by(Year) |>
  summarize(Permanent_Inflows_Rate = sum(Permanent_Inflows_Rate, na.rm = TRUE)) |>
  ggplot(aes(x = Year, y = Permanent_Inflows_Rate)) +
  geom_line(group = 1, color = "red") +
  scale_x_continuous(breaks = seq(2009, 2019, by = 1), labels = c("2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019")) +
  theme_bw() +
  labs(
    title = "Permanent Immigrants Inflows Rate from 2009 to 2019",
    x = "Year",
    y = "Permanent Immigrants Inflows Rate" 
  )

@@

```{r}
#| label: fig-2
#| fig-cap: "A graph detailing that the overall increase in Canada's permenant immigration inflow from 2009 to 2019 which is from 249292 to 341173."
#| echo: false
#| warning: false

merged_data |>
  group_by(Year) |>
  summarize(Employment_Rate = sum(Employment_Rate, na.rm = TRUE)) |>
  ggplot(aes(x = Year, y = Employment_Rate)) +
  geom_line(group = 1, color = "blue") +
  scale_x_continuous(breaks = seq(2009, 2019, by = 1), labels = c("2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019")) +
  theme_bw() +
  labs(
    title = "Employment Rate in Canada from 2009 to 2019",
    x = "Year",
    y = "Employment Rate" 
  )

@@

merged_data <-
  merged_data |>
  mutate(Permanent_Inflows_Rate = (Permanent_Inflows / Population) * 100) |>
  mutate(Centred_Employment_Rate = Employment_Rate - mean(merged_data$Employment_Rate))

merged_data_centered_model <-
  lm(
    Permanent_Inflows_Rate ~ Employment_Rate,
    data = merged_data
  )

@@

merged_data <- merged_data %>%
  mutate(Permanent_Inflows_Rate = Permanent_Inflows / Population * 100)

  ggplot(merged_data, aes(x = Employment_Rate, y = Permanent_Inflows_Rate)) +
  geom_point(alpha = 0.5) +
  geom_smooth(
    method = "lm",
    se = TRUE,
    color = "black",
    linetype = "dashed",
    formula = "y ~ x"
  ) +
  labs(
    x = "Employment Rate (percentage)",
    y = "Permanent Inflows Rate (percentage)"
  ) +
  theme_classic()

>>>>

```{r}
#| echo: false
#| warning: false

library(knitr)
kable(merged_data)

@@

merged_data |>
  group_by(Year) |>
  ggplot(aes(x = Year, y = `Permanent Inflows Rate`)) + # Use correct column name
  geom_line(group = 1, color = "red") +
  scale_x_continuous(breaks = seq(2009, 2019, by = 1), labels = c("2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019")) +
  theme_bw() +
  labs(
    title = "Permanent Immigrants Inflows Rate from 2009 to 2019",
    x = "Year",
    y = "Permanent Immigrants Inflows Rate" 
  )

@@

```{r}
#| label: fig-2
#| fig-cap: "A graph detailing that the overall increase in Canada's permenant immigration inflow from 2009 to 2019 which is from 249292 to 341173."
#| echo: false
#| warning: false
merged_data %>%
  group_by(Year) %>%
  mutate(`Employment Rate` = sum(`Employment Rate`, na.rm = TRUE)) %>%
  ggplot(aes(x = Year, y = `Employment Rate`)) +
  geom_line(group = 1, color = "blue") +
  scale_x_continuous(breaks = seq(2009, 2019, by = 1), labels = c("2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019")) +
  theme_bw() +
  labs(
    title = "Employment Rate in Canada from 2009 to 2019",
    x = "Year",
    y = "Employment Rate" 
  )

@@

merged_data <-
  merged_data |>
  mutate(Centred_Employment_Rate = `Employment Rate` - mean(merged_data$`Employment Rate`))

merged_data_centered_model <-
  lm(
    `Permanent Inflows Rate` ~ `Employment Rate`,
    data = merged_data
  )

@@

library(ggplot2)

merged_data %>%
  ggplot(aes(x = `Employment Rate`, y = `Permanent Inflows Rate`)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black", linetype = "dashed") +
  labs(x = "Employment Rate (percentage)", y = "Permanent Inflows Rate (percentage)",
       title = "Relationship between Employment Rate and Permanent Inflows Rate") +
  theme_classic()
